A numerical study of variational data assimilation for the wave equation in heterogeneous media

### 2024-03-28 tex/main.tex
Updates from Overleaf
GCC figure & Plot update

\subsection{Examples in one space dimension}

\subsubsection{Simple Example}\label{sec:numex:1D:simple}
\noindent We set $\Omega \coloneqq [0,1]$ and define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$. Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$. As a first example, we consider the following exact solution considered in \cite{MHI08}
\begin{equation}\label{eq:1D:exact:simple}
    u(x,t) := \begin{cases}
        \cos(w_1 c_1 t) \cos(w_1(x-0.5)), & x \in \Omega_1, \\
        \cos(w_2 c_2 t) \cos(w_2(x-0.5)), & x \in \Omega_2,
    \end{cases}
\end{equation}
where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$. Furthermore, we define
\begin{equation}
    \omega \coloneqq [0.0,0.25] \cup [0.75,1.0], \quad \text{and} \quad \Omega_R \coloneqq \Omega \setminus \omega = [0.25,0.75].
\end{equation}
In one space dimension, the domain $\omega_T$ fulfills the GCC if and only if $T > 2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$, where $\operatorname{dist}_c(x,\omega_T)$ denotes the distance of $x$ to $\omega_T$ with respect to the rescaled metric $d_c$. Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric. Then, we have that
\begin{equation}
    d_c(x,y) \coloneqq \mathbbm{1}_{\Omega_1} c_1(x)^{-1} d(x,y) + \mathbbm{1}_{\Omega_2} c_2(x)^{-1} d(x,y), \quad x,y \in \Omega.
\end{equation} 
Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, we require that $T > 0.25(1+c_1^{-1})$.

and \textbf{compute until $T = 1.0$, correct...} to ensure that the GCC is fulfilled. Furthermore, we set $h = 1/2^{1+L}$ and $\Delta t = h/2$ for different refinement levels $L \in \{1,2,3,4\}$. The results of the experiments can be found in Fig. \ref{fig:jumpCoefs:contrast:2.5} and Fig. \ref{fig:jumpCoefs:quality}. ... \\

\begin{figure}[!htbp]
    \begin{center}
        \begin{tikzpicture}[scale=0.72]
            \begin{groupplot}[%
                group style={%
                group size=2 by 2,
                horizontal sep=1.25cm,
                vertical sep=2cm,
                },
            ymajorgrids=true,
            grid style=dashed,
            %ymin = 1e-3, ymax = 0.5e1,
            ]    
            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T=0.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]

@@

            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]
            %L2-L2-u_t (k = 2)
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};

@@

            \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(2))^(x-0.9)};
            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
            \node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
            \legend{$k=2 $,, $k = 3$,}
            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.1$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]

@@

            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$c_1 = 2.5$, $T = 0.1$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]
            %L2-L2-u_t (k = 2)
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};

@@

            };
            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
            \legend{$k=2 $,, $k = 3$,}
            \end{groupplot}
        \end{tikzpicture}
    \end{center}
    \caption{We consider the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ for contrast $c_1 = 2.5$ (left \& middle). Both, the $L^\infty(0,T;L^2(\Omega_R))$-error of $u-u_h$ (left) and the $L^2(0,T;L^2(\Omega_R))$-error of $\dt (u-u_h)$ (middle) converge with order $\mathcal{O}(h^k)$ and are close to the respective error of the $L^2$-bestapproximation (dashed lines). For increasing contrast $c_1$, both errors increase with the same order of magnitude as the respective best approximation error (right). \textbf{left is with $T = 0.5$, the increasing contrast is still with $T = 1.0$ and not on $\Omega_R$..., also adjust the time step...}, rewrite..., plot $\mathcal{O}(\log(h))$ ... }
    \label{fig:jumpCoefs:contrast:2.5}
  \end{figure}

@@

            \end{groupplot}
        \end{tikzpicture}
        \pgfplotslegendfromname{named}
    \end{center}
    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$. We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ decreases with the constrast $c_1$ while keeping the GCC fulfilled.}
    \label{fig:jumpCoefs:increasingcontrast}
  \end{figure}

@@

            \end{groupplot}
        \end{tikzpicture}
        \pgfplotslegendfromname{named}
    \end{center}
    \caption{Exact solution and approximations with $k = 3$ on different refinement levels for $c_1 = 2.5$ (left) and $c_1= 5.5$ (right).}
    \label{fig:jumpCoefs:quality}
  \end{figure}

@@

\subsubsection{Multiple jumps}
\noindent The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$. For points $p_1,p_2 \in (0,1)$, we decompose the interval $\Omega = [0,1]$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t. $\Omega = \cup_{i = 1,2,3} \overline{\Omega}_i$. Then, we consider the following Ansatz for the exact solution: 
\begin{equation}\label{eq:1D:exact:simpleMult}
    u(x,t) := \begin{cases}
        \cos(w_1 c_1 t) \cos(w_1(x-p_1)), & x \in \Omega_1, \\
        \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3. 
    \end{cases}
\end{equation}
To ensure that the solution is continuous, we choose $p_2$ in dependence of $p_1$ and $w_2$ in the following way. We know that 
\begin{equation*}
    \cos(w_2(x-p_1)) = 1 \Leftrightarrow w_2(x-p_1) = 2 \pi n, n \in \mathbb{Z} \Leftrightarrow x = \frac{2 \pi n + w_2 p_1}{w_2}, n \in \mathbb{Z}. 
\end{equation*}
Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function \eqref{eq:1D:exact:simpleMult} is indeed continuous.  
In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$. Figure \ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ and $c_1 = 7.5$.

>>>>

\subsection{Examples in one space dimension}
\noindent We consider the unit interval $\Omega \coloneqq [0,1] \subset \mathbb{R}$. For a refinement level $L \in \mathbb{N}$, we partition the domain into $2^{L+1}$ uniform elements such that $h = 1/2^{L+1}$. The time step is chosen as $\Delta t = h$.

\subsubsection{Simple Example}\label{sec:numex:1D:simple}
\noindent We define the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$. Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$. As a first example, we consider the following exact solution \cite{MHI08}
\begin{equation}\label{eq:1D:exact:simple}
    u(x,t) := \begin{cases}
        \cos(w_1 c_1 t) \cos(w_1(x-0.5)), & x \in \Omega_1, \\
        \cos(w_2 c_2 t) \cos(w_2(x-0.5)), & x \in \Omega_2,
    \end{cases}
\end{equation}
where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$. Furthermore, we define
\begin{equation}
    \omega \coloneqq [0.0,0.25] \cup [0.75,1.0], \quad \text{and} \quad \Omega_R \coloneqq \Omega \setminus \omega = [0.25,0.75].
\end{equation}
Note that in one space dimension, the requirement \eqref{eq:Tcondition} on $T$ already implies the GCC. Let $d(x,y) \coloneqq \vert x - y \vert$, $x, y \in \Omega$, be the Euclidean metric. Then, we set
\begin{equation}
    d_c(x,y) \coloneqq \mathbbm{1}_{\Omega_1} c_1(x)^{-1} d(x,y) + \mathbbm{1}_{\Omega_2} d(x,y), \quad x,y \in \Omega.
\end{equation} 
Thus, for $\omega$ as above, $c_2 = 1$ fixed and $c_1 > 1.0$, the condition \eqref{eq:Tcondition} translates to $T > 0.25(1+c_1^{-1})$.

\begin{figure}
    \centering
    \begin{tikzpicture}[scale=3]
        \draw[-stealth] (-0.15,0) -- (1.15,0); 
        \draw[-stealth] (0,-0.15) -- (0,1.15);
        \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
        \draw[fill=gray!40,draw=none,opacity=0.5] (0,0) -- (0.5,0) -- (0.5,1) -- (0,1) -- cycle;
        \draw[-stealth] (0.5,0) -- (1,0.5) -- (0.5,1);
        \node at (-0.15,1) {\footnotesize $T$}; 
        \node at (0.75,-0.15) {\footnotesize $\sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$}; 
        \node at (1.15,0.5) {\footnotesize $t_0$};
        \draw (0.7,0) to[bend right=45] (0.65,0.15); 
        \node at (0.6,0.05) {\footnotesize $\alpha$};
        \node at (0.25,0.5) {\footnotesize $\omega_T$};
        \begin{scope}[xshift=2cm]
            \draw[-stealth] (-0.15,0) -- (1.15,0); 
            \draw[-stealth] (0,-0.15) -- (0,1.15);
            \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- cycle;
            \draw[fill=gray!40,draw=none,opacity=0.5] (0,0) -- (0.25,0) -- (0.25,1) -- (0,1) -- cycle;
            \draw[fill=gray!40,draw=none,opacity=0.5] (0.75,0) -- (1,0) -- (1,1) -- (0.75,1) -- cycle;
            \draw[-stealth] (0.25,0) -- (0.75,0.5);
            \node at (-0.15,1) {\footnotesize $T$}; 
            \node at (0.5,-0.15) {\footnotesize $2 \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$}; 
            \node at (0.67,0.5) {\footnotesize $t_0$};
            \draw (0.45,0) to[bend right=45] (0.4,0.15); 
            \node at (0.35,0.05) {\footnotesize $\alpha$};
            \node at (0.125,0.5) {\footnotesize $\omega_T$};
            \node at (0.875,0.5) {\footnotesize $\omega_T$};
        \end{scope}
    \end{tikzpicture}
    \caption{(\textbf{Can be deleted lateron, only for our own understanding:}) Illustration of the GCC and condition \eqref{eq:Tcondition} in one space dimension. The geometrical setup where the data is given only in one half of the domain is the worst case, because the ray can be reflected at the boundary. We still calculate that $1 = \tan(\alpha) = t_0 / \sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$, i.e. $T > 2 t_0 = 2\sup_{x \in \Omega} \operatorname{dist}_c(x,\omega_T)$ is required for the GCC. Note we can also assume that $c_1 = c_2 = 1$, because the metric is rescaled wrt to the wavespeed. Could probably show that the GCC and the condition on $T$ are in fact equivalent in one dimension.}
\end{figure}

\noindent Figure \ref{fig:jumpCoefs:contrast:2.5} shows that for $T$ large enough, the errors $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ and $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ converge with order $\mathcal{O}(h^k)$. In contrast, if $T$ is chosen too small such that the GCC is not satisfied, the errors do not converge optimally. 
Figures \ref{fig:jumpCoefs:quality} and \ref{fig:jumpCoefs:increasingcontrast} show that ...

\begin{figure}[!htbp]
    \begin{center}
        \begin{tikzpicture}[scale=0.72]
            \begin{groupplot}[%
                group style={%
                group size=2 by 2,
                horizontal sep=1.25cm,
                vertical sep=2cm,
                },
            ymajorgrids=true,
            grid style=dashed,
            %ymin = 1e-3, ymax = 0.5e1,
            ]    
            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T=0.5$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]

@@

            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.5$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]

            %L2-L2-u_t (k = 2)
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.5_1D_jumpingCoefs_k3.csv};

@@

            \addplot[gray, dashed, domain=1:4] {4.5*(1/2^(2))^(x-0.9)};
            %\addplot[gray, dashed, domain=1:4] {1.0*(1/2^(2))^(x-0.9)};
            \addplot[gray, dashed, domain=1:4] {1.0*(1/2^(3))^(x-0.9)};
            %\addplot[gray, dashed, domain=1:4] {0.5*(1/2^(3))^(x-0.9)};
            \node [draw=none] at (axis description cs:0.30,0.87) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
            \legend{$k=2 $,, $k = 3$,}
            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert (u - u_h) \Vert_{L^\infty(0,T;L^2(\Omega))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]

@@

            \nextgroupplot[width=8cm,height=6.2cm,domain=1:4,xmode=linear,ymode=log, ylabel={}, xlabel={$L$}, title={$T = 0.1$, $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=, 
            legend pos=south west, %yticklabels={,,},
            ]
            %L2-L2-u_t (k = 2)
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,color=orange,mark=square*] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};
            \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt,dashed,color=orange,mark=square*] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../data/simpleExact_T0.1_1D_jumpingCoefs_k3.csv};

@@

            };
            \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
            \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
            \node [draw=none] at (axis description cs:0.7,0.75) {\color{gray}\footnotesize $\!\!\mathcal{O}(\vert \log(h) \vert^{-1})$};
            \legend{$k=2 $,, $k = 3$,}
            \end{groupplot}
        \end{tikzpicture}
    \end{center}
    \caption{For the approximation of \eqref{eq:1D:exact:simple} with polynomial degree $k \in \{2,3\}$ and contrast $c_1 = 2.5$ we measure the errors $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (left) and $\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (right) and compare to the respective error of the $L^2$-bestapproximation (dashed). We consider the final time $T = 0.5$ (top) and $T = 0.1$ (bottom). The gray dashed lines indicate the observed convergence rates.}
    \label{fig:jumpCoefs:contrast:2.5}
  \end{figure}

@@

            \end{groupplot}
        \end{tikzpicture}
        \pgfplotslegendfromname{named}
    \end{center}
    \caption{For $k = 3$ and $L = 3$, we consider the errors $\Vert \dt (u-u_h) \Vert_{L^2(0,T;L^2(\Omega_R))}$ (left) and $\Vert u - u_h \Vert_{L^\infty(0,T;L^2(\Omega_R))}$ (right) for increasing contrast $c_1 \in \{1.0,1.5,...,4.5\}$. We compare the case where $T = 0.5$ is fixed for all choices of $c_1$ and the case where $T$ barely fulfills $T > 0.25(1+c_1^{-1})$.}
    \label{fig:jumpCoefs:increasingcontrast}
  \end{figure}

@@

            \end{groupplot}
        \end{tikzpicture}
        \pgfplotslegendfromname{named}
    \end{center}
    \caption{Exact solution \eqref{eq:1D:exact:simple} and approximations with $k = 3$ on refinement levels $L \{1,2,3,4 \}$ for contrasts $c_1 = 2.5$ (left) and $c_1= 5.5$ (right). The scale in the right plot indicates the mesh size $h = 1/2^{L+1}$ for the different refinement levels.}
    \label{fig:jumpCoefs:quality}
  \end{figure}

@@

\subsubsection{Multiple jumps}
\noindent The exact solution \eqref{eq:1D:exact:simple} can be extended to the case where we have multiple jumps in the wave speed $c$. For points $p_1,p_2 \in (0,1)$, we decompose $\Omega$ into three subdomains $\Omega_1 = (0,p_1)$, $\Omega_2 = (p_1,p_2)$, and $\Omega_3 = (p_2,1)$ s.t. $\Omega = \cup_{i = 1,2,3} \overline{\Omega}_i$. Then, we consider the following Ansatz for the exact solution: 
\begin{equation}\label{eq:1D:exact:simpleMult}
    u(x,t) := \begin{cases}
        \cos(w_1 c_1 t) \cos(w_1(x-p_1)), & x \in \Omega_1, \\
        \cos(w_2 c_2 t) \cos(w_2(x-p_1)), & x \in \Omega_2, \\
        \cos(w_3 c_3 t) \cos(w_3(x-p_2)), & x \in \Omega_3. 
    \end{cases}
\end{equation}
To ensure that the solution is continuous, we choose $p_2$ in dependence of $p_1$ and $w_2$ in the following way. We know that 
\begin{equation*}
    \cos(w_2(x-p_1)) = 1 \Leftrightarrow w_2(x-p_1) = 2 \pi n, n \in \mathbb{Z} \Leftrightarrow x = \frac{2 \pi n + w_2 p_1}{w_2}, n \in \mathbb{Z}. 
\end{equation*}
Thus, if we choose $p_2 = \frac{2 \pi n + w_2 p_1}{w_2}$ for some $n \in \mathbb{Z}$, the function \eqref{eq:1D:exact:simpleMult} is indeed continuous.  
In the following, we fix $c_2 = 1.0$ and choose $w_1 = 3 \pi$, $w_2 = w_1 c_1/c_2$ as above. Furthermore, we set $c_3 = c_1$, $w_3 = w_1$. 
As a first example, we choose $p_1 = 0.4$ and $n = 3$ such that $p_2 \approx 0.667$ and consider the data domain $\omega = [0.0,0.3] \times [0.7,1.0]$. Figure \ref{fig:jumpCoefs:multipleJumps} shows the exact solution and the approximation with $k = 3$ and $c_1 = 7.5$.
